If the Null Fits, You Must Omit: Measurement Artifacts Undermine Group Polarization Replications

### 2025-11-03 GroupPolarizationStatmod/paper/method.tex
method updates

To do
this we designed a web app that allows the user to try different latent
distribution parameters (Figure~\ref{fig:data-model-flow}) to seed a
hillclimbing algorithm that explores latent distribution parameter space
until it finds null parameters that look like group polarization under the
experiment's ordinal measurement procedure, or the algorithm stops after a
certain number of steps (Algorithm~\ref{alg:hillclimbing}). If the web app
finds

—latent mean and pre- and post-discussion 
variances that  loads experimental design and observation data
from a user-provided CSV file

ordinal measurements distort to look 
polarized.

@@

% \begin{figure}
%   \caption{\textbf{Shiny web application for user-guided hillclimbing to find
%   parameters that generate spurious group polarization.} This web application enables users to
% create new analyses of experimental conditions from published studies. Users 
% provide initial guesses for the algorithm to use as starting points in 
% finding variances that generate spurious group polarization. Users inspect 
% model fits provided by the algorithm, adjusting parameters if necessary, and
% mark an experimental condition as ``Plausibly spurious'' if a reasonable fit
% is indeed found.\mt{Maybe add some A, B, C guides to the figure and include
% in parentheses here to go with the text?}}
%   \centering
%     \includegraphics[width=0.75\textwidth]{Figures/Model/WebApp.png}
%   \label{fig:webapp}
% \end{figure}

>>>>

To do this we designed a web app that allows the user to try different latent
distribution parameters (Figure~\ref{fig:data-model-flow}) to seed a
hillclimbing algorithm that explores latent distribution parameter space
until it finds null parameters that look like group polarization under the
experiment's ordinal measurement procedure, or the algorithm stops after a
certain number of steps (Algorithm~\ref{alg:hillclimbing}). If the web app
finds a constant latent mean and pre- and post-discussion 
variances to specify a pre- and post-discussion opinion distributions that
generate spurious group polarization, this is communicated to the user who
can then mark the experimental condition as such.

@@
